Pilot data analysis

### 2021-01-04 pilot_data_analysis.Rmd
Make manuscript files

Creepy: visualize participant locations from Qualtrics
```{r participant_map}
library(sp)
library(leaflet)

participant_data <- read_csv("participant_data.csv")
coordinates(participant_data) <- c("Location Longitude","Location Latitude")
leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
```

>>>>

Creepy: visualize participant locations from Qualtrics
```{r participant_map}
# library(sp)
# library(leaflet)
# 
# participant_data <- read_csv("participant_data.csv")
# coordinates(participant_data) <- c("Location Longitude","Location Latitude")
# leaflet(participant_data) %>% addMarkers(label = .$`Confirm Prolific ID`) %>% addTiles()
```
